
## 📂 1. Environment Setup & Data Ingestion

First, we need to load the required library (`metafor`) and read the processed data extracted from Phase 2.

```{r}
#| label: setup-and-load
# Install readxl if you haven't: install.packages("readxl")
library(metafor)
library(readxl)
library(here)
library(dplyr)
```

## 📊 2. Data Preview

Let's read the Excel sheet and take a look at the column structures.
*(Uncomment the lines below once your Excel file has data)*

```{r}
# ==============================================================================
# 1. Load Dataset
# ==============================================================================
data_path <- here("data", "processed", "06_manually_checked_for_R.xlsx")
my_data <- read_excel(data_path)

# ==============================================================================
# 2. Preprocessing Logic
# ==============================================================================

# Locate the index range for metric columns (from 'Accuracy_Top1' to the second-to-last column)
start_idx <- which(names(my_data) == "Accuracy_Top1")
metric_cols <- names(my_data)[start_idx:(ncol(my_data) - 1)]

# Count valid numeric entries per metric (as.numeric automatically coerces "Unknown" to NA)
counts <- suppressWarnings(sapply(my_data[metric_cols], function(x) sum(!is.na(as.numeric(x)))))

# Select the metric with the highest count of valid numeric data as the single target $y$ variable
best_metric <- names(which.max(counts))

# Print the selection summary to the console
cat("🏆 Selected target $y$ variable:", best_metric, "(Valid numeric records:", max(counts), ")\n")

# ==============================================================================
# 3. Data Cleaning & Pipeline Execution
# ==============================================================================
# Pipeline: Convert target to numeric -> Filter out NAs -> Select base features + target + last column
processed_data <- my_data %>% 
  mutate(!!best_metric := suppressWarnings(as.numeric(.data[[best_metric]]))) %>% 
  filter(!is.na(.data[[best_metric]])) %>% 
  select(1:(start_idx - 1), all_of(best_metric), last_col())

# ==============================================================================
# 4. Inspection & Quality Check
# ==============================================================================
cat("\n✅ Data cleaning complete! Retained the final column:", names(processed_data)[ncol(processed_data)], "\n")
cat("Final Dataset Dimensions:", dim(processed_data)[1], "rows,", ncol(processed_data), "columns\n")

# 
```

## preprocessed varible
```{r}
# standardize columns
## Standardize the 'Num_Classes' column into a categorical variable
processed_data <- processed_data %>%
    mutate(
    # Step 1: Convert Num_Classes to numeric. 
    # The na_if() function safely converts the string "Unknown" into NA for mathematical logic.
    Num_Classes = as.numeric(na_if(Num_Classes, "Unknown")),
    
    # Step 2: Create the categorical bins (Small, Medium, Large)
    Num_Classes = case_when(
    # Force Abdaoui's massive terminology mapping tasks (SNOMED, LOINC, ICD-11) into the "Massive" bin (originally "UNknown")
        First_Author == "Abdaoui" ~ "Massive",
      
        # General binning rules based on numeric thresholds
        Num_Classes < 20 ~ "Small",
        Num_Classes >= 20 & Num_Classes <= 100 ~ "Medium",
        Num_Classes > 100 & Num_Classes <= 1000 ~ "Large",
        Num_Classes > 1000 ~ "Massive",
      
      # Catch-all for any other unhandled missing values
      TRUE ~ "Not Reported"
    ))

## standardize 'Data_Scource'
processed_data = processed_data %>% 
    mutate(Data_Source = case_when(
        grepl("MIMIC|google|IPA", Data_Source, ignore.case = TRUE)~ "Public",
        grepl("Census|IRS|SEER|NCI", Data_Source, ignore.case = TRUE)~ "Government",
        TRUE ~ "Institutional" # catch-all for Moffitt, Military, Business, UCSD, etc.
))

## Standardize the 'Avg_Text_Length' column
processed_data <- processed_data %>%
    mutate(Avg_Text_Length = case_when(
    # Catch indicators of short text: the word "Short" or small decimal numbers like "2.76", "3.78"
    grepl("Short|2\\.76|3\\.78", Avg_Text_Length, ignore.case = TRUE) ~ "Short Text",
    
    # Catch indicators of long text: specific large numbers, "tokens", "words", "Full", "Narrative"
    grepl("439|3000|500|Full|Narrative", Avg_Text_Length, ignore.case = TRUE) ~ "Long Document",
    # Fallback option just in case
    TRUE ~ "Not Reported"
  ))


```
```{r}
# 1. Identify columns with exactly 1 unique value
constant_cols <- names(processed_data)[sapply(processed_data, function(x) length(unique(na.omit(x))) == 1)]

# 2. Report the deleted column names
cat("Deleted columns:", paste(constant_cols, collapse = ", "), "\n")

# 3. Drop these columns from the dataset
modeling_data <- processed_data[, !names(processed_data) %in% constant_cols]
```

## transformation of the target varible
```{r}
y= processed_data$Accuracy_Top1
# if the metric follow normally distribution?
hist(y,
     main = "Distribution of Top-1 Accuracy", # Plot title
     xlab = "Accuracy Score",                  # X-axis label
     ylab = "Frequency",               # Y-axis
     ) 
```
```{r}
# trans 1: log transformation
hist(log(y),
     main = "Distribution of Top-1 Accuracy", # Plot title
     xlab = "Accuracy Score",                  # X-axis label
     ylab = "Frequency",               # Y-axis
     ) 
```
```{r}
````

## 🧠 3. Three-Level Meta-Analysis Modeling

We will use the `rma.mv` function from the `metafor` package to fit our three-level random-effects model. This accounts for the hierarchical structure (e.g., multiple effect sizes extracted from the same study).

```{r}
#| label: meta-model
# Example structure for 3-level meta-analysis:
# res <- rma.mv(yi = effect_size, 
#               V = sampling_variance, 
#               random = ~ 1 | study_id / effect_id, 
#               data = my_data)
# summary(res)

```

## 🌲 4. Visualizations (Forest & Funnel Plots)

Once the model is fitted, we can generate publication-quality forest plots.

```{r}
#| label: plots
# forest(res)
# funnel(res)
table(processed_data$Imbalance_Ratio,processed_data$Imbalance_Strategy)
```

```

