
## 📂 1. Environment Setup & Data Ingestion

First, we need to load the required library (`metafor`) and read the processed data extracted from Phase 2.

```{r}
#| label: setup-and-load
# Install readxl if you haven't: install.packages("readxl")
library(metafor)
library(readxl)

# Define the relative path to your processed data
# Since this file is inside 'src_03_meta_analysis/', we go up one level to find 'data/'
data_path <- "../data/processed/05_Data_Extraction_for_R.xlsx"

print(paste("Looking for data at:", data_path))
```

## 📊 2. Data Preview

Let's read the Excel sheet and take a look at the column structures.
*(Uncomment the lines below once your Excel file has data)*

```{r}
#| label: preview-data
# my_data <- read_excel(data_path)
# head(my_data)
# str(my_data)

```

## 🧠 3. Three-Level Meta-Analysis Modeling

We will use the `rma.mv` function from the `metafor` package to fit our three-level random-effects model. This accounts for the hierarchical structure (e.g., multiple effect sizes extracted from the same study).

```{r}
#| label: meta-model
# Example structure for 3-level meta-analysis:
# res <- rma.mv(yi = effect_size, 
#               V = sampling_variance, 
#               random = ~ 1 | study_id / effect_id, 
#               data = my_data)
# summary(res)

```

## 🌲 4. Visualizations (Forest & Funnel Plots)

Once the model is fitted, we can generate publication-quality forest plots.

```{r}
#| label: plots
# forest(res)
# funnel(res)

```

```

