## 📂 1. Environment Setup & Data Ingestion

First, we need to load the required packages and read the processed data extracted from Phase 2.

```{r, warning=FALSE, message=FALSE}
#| label: setup-and-load
library(metafor)
library(readxl)
library(here)
library(dplyr)
library(tidyr)
```

## 📊 2. Data Loading & Target Variable Selection

Let's read the Excel sheet and identify the performance metric with the most valid entries to serve as our target variable $y$.

```{r}
#| label: data-loading
# 1. Load Dataset
data_path <- here("data", "processed", "06_manually_checked_for_R.xlsx")
my_data <- read_excel(data_path)

# 2. Preprocessing Logic: Select best metric
start_idx <- which(names(my_data) == "Accuracy_Top1")
metric_cols <- names(my_data)[start_idx:(ncol(my_data) - 1)]

# Count valid numeric entries per metric
counts <- suppressWarnings(sapply(my_data[metric_cols], function(x) sum(!is.na(as.numeric(x)))))
best_metric <- names(which.max(counts))

cat("🏆 Selected target $y$ variable:", best_metric, "(Valid numeric records:", max(counts), ")\n")

# 3. Target Extraction & Initial Filter
processed_data <- my_data %>% 
  mutate(!!best_metric := suppressWarnings(as.numeric(.data[[best_metric]]))) %>% 
  filter(!is.na(.data[[best_metric]])) %>% 
  select(1:(start_idx - 1), all_of(best_metric), last_col())

cat("\n✅ Initial cleaning complete! Retained the final column:", names(processed_data)[ncol(processed_data)], "\n")
cat("Dimensions before feature standardization:", dim(processed_data)[1], "rows,", ncol(processed_data), "columns\n")
```

## 🧹 3. Feature Engineering & Standardization

Here we consolidate all string manipulation, data binning, and factor conversions into a single, highly efficient `dplyr` pipeline.

```{r}
#| label: data-standardization
processed_data <- processed_data %>%
  mutate(
    # --- 1. Num_Classes (Categorical Binning) ---
    Num_Classes_Numeric = as.numeric(na_if(Num_Classes, "Unknown")),
    Num_Classes = case_when(
      First_Author == "Abdaoui" ~ "Massive",
      Num_Classes_Numeric < 20 ~ "Small",
      Num_Classes_Numeric >= 20 & Num_Classes_Numeric <= 100 ~ "Medium",
      Num_Classes_Numeric > 100 & Num_Classes_Numeric <= 1000 ~ "Large",
      Num_Classes_Numeric > 1000 ~ "Massive",
      TRUE ~ "Not Reported"
    ),
    
    # --- 2. Data_Source ---
    Data_Source = case_when(
      grepl("MIMIC|google|IPA", Data_Source, ignore.case = TRUE) ~ "Public",
      grepl("Census|IRS|SEER|NCI", Data_Source, ignore.case = TRUE) ~ "Government",
      TRUE ~ "Institutional"
    ),
    
    # --- 3. Train_N (Log10 Transformation) ---
    # Safely converts "Unknown" to NA, then takes log10
    log10_Train_N = log10(as.numeric(na_if(Train_N, "Unknown"))),
    
    # --- 4. Avg_Text_Length ---
    Avg_Text_Length = case_when(
      grepl("Short|2\\.76|3\\.78", Avg_Text_Length, ignore.case = TRUE) ~ "Short Text",
      grepl("439|3000|500|Full|Narrative", Avg_Text_Length, ignore.case = TRUE) ~ "Long Document",
      TRUE ~ "Not Reported"
    ),
    
    # --- 5. Imbalance_Ratio (Severity Levels) ---
    Imbalance_Level = case_when(
      grepl("≤5|Zipfian|n<10|Top 10%|highly skewed", Imbalance_Ratio, ignore.case = TRUE) ~ 3,
      grepl("seldom reported|disproportionate", Imbalance_Ratio, ignore.case = TRUE) ~ 2,
      TRUE ~ 1
    ),
    Imbalance_Ratio = factor(
      Imbalance_Level,
      levels = c(1, 2, 3),
      labels = c("1_Low_or_Unknown", "2_Moderate", "3_Severe_LongTail"),
      ordered = TRUE
    ),
    
    # --- 6. Base_Model (Core Model Extraction) ---
    Base_Model = case_when(
      grepl("BERT", Base_Model, ignore.case = TRUE) ~ "BERT",
      grepl("T5", Base_Model, ignore.case = TRUE) ~ "T5",
      grepl("LLaMA", Base_Model, ignore.case = TRUE) ~ "LLaMA",
      grepl("MTHISAN", Base_Model, ignore.case = TRUE) ~ "MTHISAN",
      grepl("Retrieval|BEACON", Base_Model, ignore.case = TRUE) ~ "Information Retrieval",
      grepl("Logistic|LR", Base_Model, ignore.case = TRUE) ~ "Logistic Regression",
      grepl("Naïve|Bayes|MNB", Base_Model, ignore.case = TRUE) ~ "Naive Bayes",
      grepl("SVM", Base_Model, ignore.case = TRUE) ~ "SVM",
      grepl("Forest|LightGBM", Base_Model, ignore.case = TRUE) ~ "Tree Ensemble",
      grepl("Knn", Base_Model, ignore.case = TRUE) ~ "KNN",
      grepl("Lasso|Elastic|SGD|Perceptron", Base_Model, ignore.case = TRUE) ~ "Linear/Regularized",
      TRUE ~ "Other"
    ),
    
    # --- 7. Model_Approach (Flat vs Hierarchical) ---
    Model_Approach = case_when(
      grepl("Hierarchical", Model_Approach, ignore.case = TRUE) ~ "Hierarchical",
      grepl("Flat", Model_Approach, ignore.case = TRUE) ~ "Flat",
      TRUE ~ Model_Approach
    ),
    
    # --- 8. Cross-Validation (CV) ---
    CV_Applied = case_when(
      grepl("yes", CV_Applied, ignore.case = TRUE) ~ "Yes",
      grepl("no", CV_Applied, ignore.case = TRUE) ~ "No",
      TRUE ~ NA_real_
    ),
    CV_Folds = as.numeric(CV_Folds),
    
    # --- 9. Hyperparam_Tuning ---
    Hyperparam_Tuning = case_when(
      grepl("Grid Search|Grid search", Hyperparam_Tuning, ignore.case = TRUE) ~ "Grid Search",
      grepl("Manual", Hyperparam_Tuning, ignore.case = TRUE) ~ "Manual Tuning",
      grepl("Self-tuning", Hyperparam_Tuning, ignore.case = TRUE) ~ "Self-Tuning",
      grepl("Not Reported|Unknown", Hyperparam_Tuning, ignore.case = TRUE) ~ "Not Reported",
      TRUE ~ "Not Reported"
    ),
    
    # --- 10. Factorize Binary Columns ---
    Human_in_Loop = factor(Human_in_Loop, levels = c(0,1), labels = c('No','Yes')),
    Open_Source   = factor(Open_Source, levels = c(0,1), labels = c('No','Yes')),
    Hierarch_Metric = factor(Hierarch_Metric, levels = c(0,1), labels = c('No','Yes'))
  ) %>%
  
  # --- 11. Strategy Flags to Yes/No ---
  mutate(across(starts_with("Strategy_"), ~ ifelse(. == 1, "Yes", "No"))) %>%
  
  # Clean up intermediate calculation columns
  select(-Num_Classes_Numeric, -Imbalance_Level, -Train_N) 
```

## ✂️ 4. Drop Zero-Variance Columns

Remove any columns that ended up having exactly 1 unique value across the entire dataset, as they provide no variance for statistical modeling.

```{r}
#| label: drop-constant-cols
# Identify columns with exactly 1 unique value (ignoring NAs)
constant_cols <- names(processed_data)[sapply(processed_data, function(x) length(unique(na.omit(x))) == 1)]

cat("🗑️ Deleted columns due to zero variance:", paste(constant_cols, collapse = ", "), "\n")

# Drop these columns to create the final modeling dataset
modeling_data <- processed_data %>% select(-all_of(constant_cols))
```

## 📈 5. Target Variable Distribution & Transformation

Checking the distribution of our target accuracy variable to see if standardizations (Logit or Arcsine Square Root) improve normality for Meta-Regression.

```{r, fig.width=12, fig.height=4}
#| label: target-distribution
y <- modeling_data[[best_metric]]

# Set up a 1x3 grid for side-by-side comparison
par(mfrow = c(1, 3))

# 1. Raw Distribution
hist(y, col="skyblue", border="white",
     main = "Raw Distribution", 
     xlab = "Accuracy Score", ylab = "Frequency") 

# 2. Logit Transformation
hist(log(y/(1-y)), col="lightgreen", border="white",
     main = "Logit Transformation", 
     xlab = "Logit(Accuracy)", ylab = "Frequency") 

# 3. Arcsine Square Root Transformation
hist(asin(sqrt(y)), col="salmon", border="white",
     main = "Arcsine Sqrt Transformation", 
     xlab = "Asin(Sqrt(Accuracy))", ylab = "Frequency")

# Reset layout
par(mfrow = c(1, 1))
```

## 🧠 6. Three-Level Meta-Analysis Modeling

We will use the `rma.mv` function from the `metafor` package to fit our three-level random-effects model. This accounts for the hierarchical structure (e.g., multiple effect sizes extracted from the same study).

```{r}
#| label: meta-model
#| label: meta-model-null-manual

# ==============================================================================
# 1. Manual Calculation of Effect Size (Logit) and Sampling Variance
# ==============================================================================
# Instead of using escalc(), we manually compute the logit-transformed 
# proportions (yi) and their corresponding sampling variances (vi).
# Mathematical formulas:
# yi = ln(p / (1 - p))
# vi = 1 / (n * p * (1 - p))

modeling_data <- modeling_data %>%
  mutate(
    Test_N = as.numeric(Test_N),
    p = Accuracy_Top1
  ) %>%
  filter(!is.na(Test_N) & !is.na(p)) %>%
  mutate(
    # Safety boundary: Prevent log(0) or division by zero if any model 
    # reported exactly 1.0 (100%) or 0.0 accuracy.
    p_adj = case_when(
      p == 1.0 ~ 0.9999,
      p == 0.0 ~ 0.0001,
      TRUE ~ p
    ),
    
    # Calculate Logit Effect Size (yi)
    yi = log(p_adj / (1 - p_adj)),
    
    # Calculate Sampling Variance (vi)
    vi = 1 / (Test_N * p_adj * (1 - p_adj))
  )

# ==============================================================================
# 2. Fit the Three-Level Null Meta-Analysis Model
# ==============================================================================
# Fit an intercept-only (null) model in the Logit space.
# Random effects structure accounts for dependencies within the same paper.
# Level 3: First_Author (Between-study variance)
# Level 2: Trial (Between-model variance within the same study)

res_null <- rma.mv(yi = yi, 
                   V = vi, 
                   random = ~ 1 | First_Author / Trial, 
                   data = modeling_data)

# Print the model summary (Logit Scale)
cat("--- Null Model Results (Logit Scale) ---\n")
summary(res_null)

# ==============================================================================
# 3. Back-transformation to Original Accuracy Scale
# ==============================================================================
# Use the inverse logit function to convert the pooled estimate and CIs 
# back to a 0-1 proportion.

cat("\n\n--- Pooled Accuracy (Back-transformed to 0-1 scale) ---\n")
predict(res_null, transf = transf.ilogit)

# ==============================================================================
# Calculate I^2 (Variance Proportions) for the 3-Level Meta-Analysis
# ==============================================================================

# 1. 提取三层的方差 (Variance components)
sigma2_3 <- res_null$sigma2[1] # Level 3 (First_Author)
sigma2_2 <- res_null$sigma2[2] # Level 2 (Trial)

# 2. 计算 Level 1 的典型抽样误差 (Typical sampling variance, v)
# 采用 Higgins & Thompson (2002) 的经典近似算法
wi <- 1 / modeling_data$vi
k <- length(wi)
v_typical <- (k - 1) / (sum(wi) - (sum(wi^2) / sum(wi)))

# 3. 计算三层的总方差
total_variance <- sigma2_3 + sigma2_2 + v_typical

# 4. 计算并打印 I^2 百分比
I2_Level3 <- (sigma2_3 / total_variance) * 100
I2_Level2 <- (sigma2_2 / total_variance) * 100
I2_Level1 <- (v_typical / total_variance) * 100

cat("--- Distribution of Variance (I^2 in 3-Level Model) ---\n")
cat(sprintf("Level 3 (Between-Study / First_Author) : %.2f%%\n", I2_Level3))
cat(sprintf("Level 2 (Within-Study / Trial)         : %.2f%%\n", I2_Level2))
cat(sprintf("Level 1 (Sampling Error)               : %.2f%%\n", I2_Level1))
cat(sprintf("Total True Heterogeneity (I^2)         : %.2f%%\n", I2_Level3 + I2_Level2))
```


## 🌲 7. Visualizations & Crosstabs

Once the model is fitted, we can generate publication-quality forest plots. We can also inspect interactions between categorical predictors.

```{r}
#| label: plots-and-tables
# forest(res)
# funnel(res)

# Cross-tabulation example
table(modeling_data$Imbalance_Ratio, modeling_data$Imbalance_Strategy)
```