---
title: "Multi-level Meta-Analysis and Meta-Regression"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: flatly
    highlight: tango
---

# 📂 1. Environment Setup & Data Ingestion

First, we need to load the required packages and read the processed data extracted from Phase 2.

```{r setup-and-load, warning=FALSE, message=FALSE}
library(metafor)
library(readxl)
library(here)
library(dplyr)
library(tidyr)
```

# 📊 2. Data Loading & Target Variable Selection

Let's read the Excel sheet and identify the performance metric with the most valid entries to serve as our target variable.

```{r data-loading}
# 1. Load Dataset
data_path <- here("data", "processed", "06_manually_checked_for_R.xlsx")
my_data <- read_excel(data_path)

# 2. Preprocessing Logic: Select best metric
start_idx <- which(names(my_data) == "Accuracy_Top1")
metric_cols <- names(my_data)[start_idx:(ncol(my_data) - 1)]

# Count valid numeric entries per metric
counts <- suppressWarnings(sapply(my_data[metric_cols], function(x) sum(!is.na(as.numeric(x)))))
best_metric <- names(which.max(counts))

cat("🏆 Selected target variable:", best_metric, "(Valid numeric records:", max(counts), ")\n")

# 3. Target Extraction & Initial Filter
processed_data <- my_data %>% 
  mutate(!!best_metric := suppressWarnings(as.numeric(.data[[best_metric]]))) %>% 
  filter(!is.na(.data[[best_metric]])) %>% 
  select(1:(start_idx - 1), all_of(best_metric), last_col())

cat("\n✅ Initial cleaning complete! Retained the final column:", names(processed_data)[ncol(processed_data)], "\n")
cat("Dimensions before feature standardization:", dim(processed_data)[1], "rows,", ncol(processed_data), "columns\n")
```

# 🧹 3. Feature Engineering & Standardization

Here we consolidate all string manipulation, data binning, and factor conversions into a single, highly efficient `dplyr` pipeline.

```{r data-standardization}
processed_data <- processed_data %>%
  mutate(
    # --- 1. Num_Classes (Categorical Binning) ---
    Num_Classes_Numeric = as.numeric(na_if(Num_Classes, "Unknown")),
    Num_Classes = factor(
      case_when(
        # in my case, all 'NA' in a paper, manually label them as "Massive"
        First_Author == "Abdaoui" ~ "Massive", 
        Num_Classes_Numeric < 20 ~ "Small",
        Num_Classes_Numeric >= 20 & Num_Classes_Numeric <= 100 ~ "Medium",
        Num_Classes_Numeric > 100 & Num_Classes_Numeric <= 1000 ~ "Large",
        Num_Classes_Numeric > 1000 ~ "Massive"
      ),
      levels = c("Small", "Medium", "Large", "Massive"),
      ordered = TRUE
    ),
    
    # --- 2. Data_Source ---
    Data_Source = case_when(
      grepl("MIMIC|google|IPA", Data_Source, ignore.case = TRUE) ~ "Open_Non_Gov",
      grepl("Census|IRS|SEER|NCI", Data_Source, ignore.case = TRUE) ~ "Regulated_Gov",
      TRUE ~ "Private"
    ),
    
    # --- 3. Train_N (Log10 Transformation) ---
    # Safely converts "Unknown"(non-numeric) to NA, then takes log10
    Train_N = log10(as.numeric((Train_N))),
    
    # --- 4. Avg_Text_Length ---
    Avg_Text_Length = case_when(
      grepl("Short|2\\.76|3\\.78", Avg_Text_Length, ignore.case = TRUE) ~ "Short Text",
      grepl("439|3000|500|Full|Narrative", Avg_Text_Length, ignore.case = TRUE) ~ "Long Document",
      TRUE ~ "Not Reported"
    ),
    
    # --- 5. Imbalance_Ratio (Severity Levels) ---
    Imbalance_Ratio = case_when(
      grepl("≤5|Zipfian|n<10|Top 10%|highly skewed", Imbalance_Ratio, ignore.case = TRUE) ~ "3_Severe_LongTail",
      grepl("seldom reported|disproportionate|Max freq 8, Min freq 2 occurrences", Imbalance_Ratio, ignore.case = TRUE) ~ "2_Moderate",
      grepl("Unknown|Not Reported", Imbalance_Ratio, ignore.case = TRUE) ~ 'Unknown',
      TRUE ~ "1_balanced"
    ),
    
    # --- 6. Base_Model (Core Model Extraction) ---
    Base_Model = case_when(
      grepl("BERT", Base_Model, ignore.case = TRUE) ~ "BERT",
      grepl("T5", Base_Model, ignore.case = TRUE) ~ "T5",
      grepl("LLaMA", Base_Model, ignore.case = TRUE) ~ "LLaMA",
      grepl("MTHISAN", Base_Model, ignore.case = TRUE) ~ "MTHISAN",
      grepl("Retrieval|BEACON", Base_Model, ignore.case = TRUE) ~ "Information Retrieval",
      grepl("Logistic|LR", Base_Model, ignore.case = TRUE) ~ "Logistic Regression",
      grepl("Naïve|Bayes|MNB", Base_Model, ignore.case = TRUE) ~ "Naive Bayes",
      grepl("SVM", Base_Model, ignore.case = TRUE) ~ "SVM",
      grepl("Forest|LightGBM", Base_Model, ignore.case = TRUE) ~ "Tree Ensemble",
      grepl("Knn", Base_Model, ignore.case = TRUE) ~ "KNN",
      grepl("Lasso|Elastic|SGD|Perceptron", Base_Model, ignore.case = TRUE) ~ "Linear/Regularized",
      TRUE ~ "Other"
    ),
    
    # --- 7. Model_Approach (Flat vs Hierarchical) ---
    Model_Approach = case_when(
      grepl("Hierarchical", Model_Approach, ignore.case = TRUE) ~ "Hierarchical",
      grepl("Flat", Model_Approach, ignore.case = TRUE) ~ "Flat",
      TRUE ~ Model_Approach
    ),
    
    # --- 8. Cross-Validation (CV) ---
    CV_Applied = case_when(
      grepl("yes", CV_Applied, ignore.case = TRUE) ~ "Yes",
      grepl("no", CV_Applied, ignore.case = TRUE) ~ "No",
      TRUE ~ 'Not reported'
    ),
    CV_Folds = as.numeric(CV_Folds),
    
    # --- 9. Hyperparam_Tuning ---
    Hyperparam_Tuning = case_when(
      grepl("Grid Search|Grid search", Hyperparam_Tuning, ignore.case = TRUE) ~ "Grid Search",
      grepl("Manual", Hyperparam_Tuning, ignore.case = TRUE) ~ "Manual Tuning",
      grepl("Self-tuning", Hyperparam_Tuning, ignore.case = TRUE) ~ "Self-Tuning",
      grepl("Not Reported|Unknown", Hyperparam_Tuning, ignore.case = TRUE) ~ "Not Reported",
      TRUE ~ "Not Reported"
    ),
    
    # --- 10. Factorize Binary Columns ---
    Human_in_Loop = factor(Human_in_Loop, levels = c(0,1), labels = c('No','Yes')),
    Open_Source   = factor(Open_Source, levels = c(0,1), labels = c('No','Yes')),
    Hierarch_Metric = factor(Hierarch_Metric, levels = c(0,1), labels = c('No','Yes'))
  ) %>%
  
  # --- 11. Strategy Flags to Yes/No ---
  mutate(across(starts_with("Strategy_"), ~ ifelse(. == 1, "Yes", "No"))) %>%
  
  # rename train size since it was log-transformed
  rename(log10_Train_N = Train_N) %>%
  
  # Clean up intermediate calculation columns
  select(-Num_Classes_Numeric)
```

# 🗑️ 4. Data Quality Control: Zero-Variance & Missingness

Remove columns that have exactly 1 unique value (no variance) or exceptionally high missingness, as they provide no information for statistical modeling.

```{r drop-constant-cols}
# Identify columns with exactly 1 unique value (ignoring NAs)
constant_cols <- names(processed_data)[sapply(processed_data, function(x) length(unique(na.omit(x))) == 1)]

cat("🗑️ Deleted columns due to zero variance:", paste(constant_cols, collapse = ", "), "\n")

# Drop these columns to create the final modeling dataset
modeling_data <- processed_data %>% select(-all_of(constant_cols))

# Factors transformation
modeling_data <- modeling_data %>% 
  mutate(across(where(is.character), as.factor))

# Drop High Missingness & Low Variance Variables First
cleaned_data <- modeling_data %>% select(
  -Prompt_Engineering,    # 92.5% Missing / Zero Variance
  -CV_Folds,              # 83.3% Missing
  -Strategy_Data_level,   # near zero variance (No: 51 Yes: 3)
  -Open_Source,           # near zero variance (No: 51 Yes: 3)
  -Taxonomy_Structure,    # near zero variance (hierarchical: 49 flat: 5)
  -Model_Approach         # near zero variance (Flat: 49 Hierarchical: 5 )
) 

# clear view
summary(cleaned_data)
```

# 🚨 5. Structural Checks: Resolving Single-Author Nesting

This scan detects if any category belongs EXCLUSIVELY to a single author. Such nesting makes it impossible for `rma.mv` to distinguish the fixed effect of the category from the random effect of the author, causing fatal singularities.

```{r check-nesting}
cat("\n=================================================================\n")
cat(" 🚨 STAGE 2: SINGLE-AUTHOR NESTED CATEGORY CHECK\n")
cat("=================================================================\n")

# Extract all categorical variables
cat_vars <- cleaned_data %>% 
  select(where(is.character) | where(is.factor)) %>%
  select(-any_of(c("DOI", "First_Author", "Trial")))

found_nested_vars <- FALSE

for (col_name in names(cat_vars)) {
  
  # Create a cross-tabulation of First_Author vs the current variable
  cross_tab <- table(cleaned_data$First_Author, cat_vars[[col_name]])
  
  # Calculate how many distinct authors use each category
  authors_per_cat <- colSums(cross_tab > 0)
  
  # Find categories that exist in exactly ONE author
  nested_cats <- names(authors_per_cat)[authors_per_cat == 1]
  
  if (length(nested_cats) > 0) {
    found_nested_vars <- TRUE
    cat(sprintf("\n⚠️ WARNING: Variable [%s] has categories strictly nested within a single author!\n", col_name))
    
    for (cat_name in nested_cats) {
      author_name <- rownames(cross_tab)[cross_tab[, cat_name] > 0]
      n_samples <- cross_tab[author_name, cat_name]
      cat(sprintf("   👉 Category '%s' (n = %d) is 100%% exclusive to author '%s'.\n", 
                  cat_name, n_samples, author_name))
    }
    
    cat(sprintf("\n📊 Full Distribution Table for [%s] across Authors:\n", col_name))
    print(cross_tab)
    cat("-----------------------------------------------------------------\n")
  }
}

if (!found_nested_vars) {
  cat("✅ PASSED! No single-author nested categories detected.\n")
}
```

### 🛠️ Recode & Merge Variables to Resolve Nesting

```{r recode-nesting}
cleaned_data <- cleaned_data %>%
  mutate(
    # 1. Domain: Medical (disease) vs Non-Medical
    Domain = factor(case_when(
      grepl("disease", Domain, ignore.case = TRUE) ~ "Medical",
      TRUE ~ "Non-Medical"
    )),
    
    # 2. Language: English vs Non-English
    Language = factor(case_when(
      grepl("english", Language, ignore.case = TRUE) ~ "English",
      TRUE ~ "Non-English"
    )),
    
    # 3. Taxonomy_Depth: Combine Top_Level and Intermediate
    Taxonomy_Depth = factor(case_when(
      Taxonomy_Depth %in% c("Top_Level", "Intermediate") ~ "Reduced_Depth",
      TRUE ~ "Full_Resolution"
    )),
    
    # 4. NLP_Era: Group into broad historical paradigms
    NLP_Era = factor(case_when(
      NLP_Era %in% c("Traditional ML", "Deep Learning (pre-PLM)") ~ "Pre-Transfer",
      NLP_Era %in% c("PLM", "LLM") ~ "Transfer-Based",
      TRUE ~ as.character(NLP_Era) 
    )),
    
    # 5. Hyperparam_Tuning: Binary grouping to absorb single-author categories
    Hyperparam_Tuning = factor(case_when(
      Hyperparam_Tuning == "Not Reported" ~ "Not_Reported",
      TRUE ~ "Reported_Tuning"
    ))
  )

cat("\n✅ Data transformation complete. Current dimensions:", dim(cleaned_data), "\n")
```

# 🧩 6. Collinearity Diagnosis & Feature Reduction

Using Cramer's V heatmap to find perfectly correlated categorical features, followed by VIF tests to ensure model stability.

```{r cramers-v-heatmap, fig.width=10, fig.height=10}
library(corrplot)

cat_vars <- cleaned_data %>% 
  select(where(is.factor) | where(is.character)) %>%
  select(-any_of(c("DOI", "First_Author", "Trial")))

n <- ncol(cat_vars)
cramer_matrix <- matrix(1, nrow = n, ncol = n, 
                        dimnames = list(names(cat_vars), names(cat_vars)))

for (i in 1:(n - 1)) {
  for (j in (i + 1):n) {
    tbl <- table(cat_vars[[i]], cat_vars[[j]])
    chi2 <- suppressWarnings(chisq.test(tbl, correct = FALSE)$statistic)
    v <- sqrt(chi2 / (sum(tbl) * min(nrow(tbl) - 1, ncol(tbl) - 1)))
    cramer_matrix[i, j] <- cramer_matrix[j, i] <- ifelse(is.na(v) || is.nan(v), 0, v)
  }
}

corrplot(cramer_matrix, 
         method = "color", type = "upper", tl.col = "black", tl.srt = 45, 
         addCoef.col = "darkgray", number.cex = 0.6, 
         title = "Categorical Feature Association (Cramer's V)", mar = c(0, 0, 2, 0))
```

### 🤖 Auto-Cluster Collinear Variables (Lightweight Strict Grouping)

```{r variable-clustering-light}
var_names <- colnames(cramer_matrix)
unvisited <- var_names
cluster_id_counter <- 1
final_clusters <- list()

# Loop until all variables have been checked
while(length(unvisited) > 0) {
  # 1. Select the first unassigned variable as the "target" (cluster anchor)
  target <- unvisited[1]
  
  # 2. Find all candidate variables with a correlation > 0.99 with the target
  candidates <- var_names[cramer_matrix[target, ] > 0.99 & !is.na(cramer_matrix[target, ])]
  
  # 3. Strict mutual-check mechanism (must be strictly > 0.99 with ALL existing members)
  strict_group <- c(target)
  for (cand in candidates) {
    if (cand != target) {
      # Check if the candidate is highly correlated with EVERY variable currently in the strict group
      if (all(cramer_matrix[cand, strict_group] > 0.99, na.rm = TRUE)) {
        strict_group <- c(strict_group, cand)
      }
    }
  }
  
  # 4. If this strict group has more than 1 variable, record it as a valid cluster
  if (length(strict_group) > 1) {
    cluster_df <- data.frame(
      Cluster_ID = paste0("Cluster_", cluster_id_counter),
      Variable   = strict_group,
      # Calculate Degrees of Freedom (DF)
      DF         = sapply(strict_group, function(x) length(unique(na.omit(cleaned_data[[x]]))) - 1),
      stringsAsFactors = FALSE
    )
    
    # Sort by DF in ascending order to make selection easier
    cluster_df <- cluster_df[order(cluster_df$DF), ]
    final_clusters[[length(final_clusters) + 1]] <- cluster_df
    cluster_id_counter <- cluster_id_counter + 1
  }
  
  # 5. Remove the grouped variables from the unvisited list and proceed to the next round
  unvisited <- setdiff(unvisited, strict_group)
}

# 6. Print the final clean report
if (length(final_clusters) > 0) {
  cluster_report <- do.call(rbind, final_clusters)
  cat("\n🔍 LIGHTWEIGHT COLLINEAR CLUSTERS (Strict Mutually V > 0.99) 🔍\n")
  cat("=================================================================\n")
  print(cluster_report, row.names = FALSE)
  cat("=================================================================\n")
} else {
  cat("✅ Clean space! No redundant clusters detected.\n")
}
```

### Drop redundant predictor based on heatmap clusters

```{r}
cleaned_data <- cleaned_data  %>%
  select(
    -Class_System,         # cluster 1,2,4,5
    -Human_in_Loop,        # cluster 3
    -Base_Model,           # cluster 6,7
    -Feature_Extraction,   # cluster 6
    -Adaptation_Strategy   # cluster 7
)
```

### 📉 Variance Inflation Factor (VIF) Checks

```{r vif-checks}
library(car)
# current predictors
lm_vif_clean_v1 <- lm(Accuracy_Top1 ~ Domain + Taxonomy_Depth + Classification_Logic +
                        Num_Classes + Data_Source  + Language + log10_Train_N +
                        Avg_Text_Length + Imbalance_Ratio + Strategy_Cost_Sensitive +
                        Strategy_Taxonomy_Mod + Strategy_Post_Hoc + Strategy_None  + NLP_Era + Domain_Specific + CV_Applied + Hyperparam_Tuning,
                      data = cleaned_data)
# Delete 'log10_Train_N' and ‘Domian’ based on earlier checks
lm_vif_clean_v2 <- lm(Accuracy_Top1 ~ Taxonomy_Depth + Classification_Logic +
                        Num_Classes + Data_Source  + Language  + Avg_Text_Length + Imbalance_Ratio + Strategy_Cost_Sensitive +
                        Strategy_Taxonomy_Mod + Strategy_Post_Hoc + Strategy_None  + NLP_Era + Domain_Specific + CV_Applied + Hyperparam_Tuning,
                      data = cleaned_data)
```
```{r}
# Further reduced features by removing 'Avg_Text_Length','language', 'strategy_none' and 'NLP_Era' to optimize VIF thresholds
lm_vif_clean_v3 <- lm(Accuracy_Top1 ~ Taxonomy_Depth + Classification_Logic +
                        Num_Classes + Data_Source   + Imbalance_Ratio + Strategy_Cost_Sensitive +
                        Strategy_Taxonomy_Mod + Strategy_Post_Hoc  + Domain_Specific + CV_Applied + Hyperparam_Tuning,
                      data = cleaned_data)
# make sure all GVIF^(1/(2*Df)) are smaller than ?
vif(lm_vif_clean_v1)
vif(lm_vif_clean_v2)
vif(lm_vif_clean_v3)
```

# 📈 7. Target Variable Transformation: Logit Scale

Checking the distribution of our target accuracy variable to verify transformations for Meta-Regression.

```{r target-distribution, fig.width=12, fig.height=4}
y <- modeling_data[[best_metric]]

par(mfrow = c(1, 3))
hist(y, col="skyblue", border="white", main = "Raw Distribution", xlab = "Accuracy Score", ylab = "Frequency") 
hist(log(y/(1-y)), col="lightgreen", border="white", main = "Logit Transformation", xlab = "Logit(Accuracy)", ylab = "Frequency") 
hist(asin(sqrt(y)), col="salmon", border="white", main = "Arcsine Sqrt Transformation", xlab = "Asin(Sqrt(Accuracy))", ylab = "Frequency")
par(mfrow = c(1, 1))
```

```{r effect-size-calc}
cleaned_data <- cleaned_data %>%
  mutate(
    Test_N = as.numeric(Test_N),
    p = Accuracy_Top1
  ) %>%
  filter(!is.na(Test_N) & !is.na(p)) %>%
  mutate(
    # Safety boundary: Prevent log(0) or division by zero for perfect scores
    p_adj = case_when(
      p == 1.0 ~ 0.9999,
      p == 0.0 ~ 0.0001,
      TRUE ~ p
    ),
    
    # Calculate Logit Effect Size (yi)
    yi = log(p_adj / (1 - p_adj)),
    
    # Calculate Sampling Variance (vi)
    vi = 1 / (Test_N * p_adj * (1 - p_adj))
  )
```

# 🏆 8. Stepwise Meta-Regression Model Selection

Finding the Optimal Model by progressively selecting the strongest predictors based on Likelihood/BIC via Maximum Likelihood (ML) estimation.

```{r step-selection-rounds}
candidate_vars <- c("Taxonomy_Depth",        
 "Classification_Logic" ,"Num_Classes", "Data_Source"   , "Language",           "Avg_Text_Length",    "Imbalance_Ratio"   ,     
"Strategy_Cost_Sensitive", "Strategy_Taxonomy_Mod" , 
 "Strategy_Post_Hoc" ,      "Strategy_None"  ,        
"NLP_Era"     ,            "Domain_Specific" ,      
"CV_Applied"     ,         "Hyperparam_Tuning" 
)
```
```{r}
# --- Base Null Model ---
null_model <- rma.mv(yi = yi, V = vi, mods = ~ 1, 
                     random = ~ 1 | First_Author / Trial, 
                     method = "ML", data = cleaned_data,
                     control = list(iter.max = 30, rel.tol = 1e-5))
cat("🎯 [Baseline] Null Model BIC =", round(BIC(null_model), 2), "\n\n")

# --- Round 1 ---
r1_results <- data.frame(Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)
for (var in candidate_vars) {
  fmla <- as.formula(paste("yi ~", var))
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  if (!is.null(mdl)) r1_results <- rbind(r1_results, data.frame(Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
}
cat("📊 ROUND 1 LEADERBOARD (Look for the LOWEST BIC):\n")
print(r1_results %>% arrange(BIC), row.names = FALSE)
```
```{r}
# --- Round 2 (Pairing Winner: Strategy_None) ---
current_model_vars <- c("Strategy_None") 
remaining_vars <- setdiff(candidate_vars, current_model_vars)
r2_results <- data.frame(Added_Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)
for (var in remaining_vars) {
  test_vars <- c(current_model_vars, var)
  fmla <- as.formula(paste("yi ~", paste(test_vars, collapse = " + ")))
  if (any(is.na(coef(lm(fmla, data = cleaned_data))))) next
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  if (!is.null(mdl)) r2_results <- rbind(r2_results, data.frame(Added_Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
}
cat("\n📊 ROUND 2 LEADERBOARD:\n")
print(r2_results %>% arrange(BIC), row.names = FALSE)
```
```{r}
# --- Round 3 (Forcing Strategy_None + Imbalance_Ratio) ---
current_model_vars <- c("Strategy_None", "Imbalance_Ratio") 
remaining_vars <- setdiff(candidate_vars, current_model_vars)
r3_results <- data.frame(Added_Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)
for (var in remaining_vars) {
  test_vars <- c(current_model_vars, var)
  fmla <- as.formula(paste("yi ~", paste(test_vars, collapse = " + ")))
  if (any(is.na(coef(lm(fmla, data = cleaned_data))))) next
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  if (!is.null(mdl)) r3_results <- rbind(r3_results, data.frame(Added_Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
}
cat("\n📊 ROUND 3 LEADERBOARD:\n")
print(r3_results %>% arrange(BIC), row.names = FALSE)
```
```{r}
# --- Round 4 (Forcing Strategy_None + Imbalance_Ratio + Data_Source) ---
current_model_vars <- c("Strategy_None", "Imbalance_Ratio", "Data_Source") 
remaining_vars <- setdiff(candidate_vars, current_model_vars)
r4_results <- data.frame(Added_Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)
for (var in remaining_vars) {
  test_vars <- c(current_model_vars, var)
  fmla <- as.formula(paste("yi ~", paste(test_vars, collapse = " + ")))
  if (any(is.na(coef(lm(fmla, data = cleaned_data))))) next
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  if (!is.null(mdl)) r4_results <- rbind(r4_results, data.frame(Added_Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
}
cat("\n📊 ROUND 4 LEADERBOARD:\n")
print(r4_results %>% arrange(BIC), row.names = FALSE)
```
```{r}
# --- Round 5 (Forcing Quad-Squad) ---
current_model_vars <- c("Strategy_None", "Imbalance_Ratio", "Data_Source", "Hyperparam_Tuning") 
remaining_vars <- setdiff(candidate_vars, current_model_vars)
r5_results <- data.frame(Added_Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)
for (var in remaining_vars) {
  test_vars <- c(current_model_vars, var)
  fmla <- as.formula(paste("yi ~", paste(test_vars, collapse = " + ")))
  if (any(is.na(coef(lm(fmla, data = cleaned_data))))) next
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  if (!is.null(mdl)) r5_results <- rbind(r5_results, data.frame(Added_Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
}
cat("\n📊 ROUND 5 LEADERBOARD:\n")
print(r5_results %>% arrange(BIC), row.names = FALSE)
```

# ⚖️ 9. Final Model Inference & Comparisons

After finding our Optimal Model (4 predictors), we evaluate it globally. Comparisons use ML, but the final output coefficients require REML + Knapp-Hartung for rigorous small-sample inference.

```{r model-comparisons}
cat("==============================================================================\n")
cat("⏳ Fitting Null, Optimal, and Full Models using 'ML' Method safely...\n")
cat("==============================================================================\n")

# 1. Null Model (ML version for comparison)
model_null_ml <- rma.mv(yi = yi, V = vi, mods = ~ 1, 
                        random = ~ 1 | First_Author / Trial, 
                        method = "ML", data = cleaned_data)

# 2. Optimal Model (Your 4 stepwise winners in ML)
fmla_optimal <- as.formula("yi ~ Strategy_None + Imbalance_Ratio + Data_Source + Hyperparam_Tuning")
model_optimal_ml <- rma.mv(yi = yi, V = vi, mods = fmla_optimal, 
                           random = ~ 1 | First_Author / Trial, 
                           method = "ML", data = cleaned_data)
```
```{r}
# 3. Full Model (All 15 stable predictors to show global variance)
fmla_full <- as.formula("yi ~ Taxonomy_Depth + Classification_Logic +
                        Num_Classes + Data_Source  + Language  + Avg_Text_Length + Imbalance_Ratio + Strategy_Cost_Sensitive +
                        Strategy_Taxonomy_Mod + Strategy_Post_Hoc + Strategy_None  + NLP_Era + Domain_Specific + CV_Applied + Hyperparam_Tuning")
model_full_ml <- rma.mv(yi = yi, V = vi, mods = fmla_full, 
                        random = ~ 1 | First_Author / Trial, 
                        method = "ML", data = cleaned_data)

cat("\n🏆 MODEL COMPARISON RESULTS (LRT via ML) 🏆\n")
anova(model_null_ml, model_optimal_ml)
anova(model_optimal_ml, model_full_ml)
anova(model_null_ml, model_full_ml)
# BIC: FULL model 197.8309, Optimal 181.4684 , Null 195.6626
```

### 🌟 Optimal: Final Publication Model (REML + KH)

```{r optimal-model}
cat("\n==============================================================================\n")
cat("🔥 RUNNING BEST MODEL: Standard REML with Knapp-Hartung (test='knha')\n")
cat("==============================================================================\n")
cleaned_data$Strategy_None <- relevel(factor(cleaned_data$Strategy_None), ref = "Yes")
cleaned_data$Imbalance_Ratio <- relevel(factor(cleaned_data$Imbalance_Ratio), ref = "3_Severe_LongTail")
# Refit using REML with Knapp-Hartung adjustment (The gold standard for small k)
rescue_model <- rma.mv(yi = yi, V = vi, mods = fmla_optimal, 
                       random = ~ 1 | First_Author / Trial, 
                       method = "REML", test = "knha", 
                       data = cleaned_data)

# Print the real publication table
print(rescue_model)
# Back-transformation to Original Accuracy Scale (0-1 proportion)
cat("\n\n--- Pooled Accuracy (Back-transformed to 0-1 scale) ---\n")
predict(rescue_model, newmods=c(1,0,0,0,1,1), transf = transf.ilogit)
```

### Univariable Sensitivity Test
```{r}
test_model <- rma.mv(yi = yi, V = vi, 
                     mods = ~ Imbalance_Ratio, # delate Data_Source, Strategy, hyperparam
                     random = ~ 1 | First_Author / Trial, 
                     method = "REML", test = "knha", 
                     data = cleaned_data)
test_model
```

### Full model output 
```{r}
full_model <- rma.mv(yi = yi, V = vi, mods = fmla_full, 
                       random = ~ 1 | First_Author / Trial, 
                       method = "REML", test = "knha", 
                       data = cleaned_data)
full_model
```

# 🧠 10. Baseline Three-Level Meta-Analysis

We use the `rma.mv` function to fit our three-level random-effects model. This accounts for the hierarchical structure (e.g., multiple effect sizes extracted from the same study).

```{r null-reml}
# Fit an intercept-only (null) model in the Logit space using REML for inference.
# Level 3: First_Author (Between-study variance)
# Level 2: Trial (Between-model variance within the same study)
res_null <- rma.mv(yi = yi, 
                   V = vi, 
                   random = ~ 1 | First_Author / Trial, 
                   data = cleaned_data,
                   method = "REML", test = "knha")

cat("--- Null Model Results (Logit Scale) ---\n")
summary(res_null)

# Back-transformation to Original Accuracy Scale (0-1 proportion)
cat("\n\n--- Pooled Accuracy (Back-transformed to 0-1 scale) ---\n")
predict(res_null, transf = transf.ilogit)
```

### 🧮 Calculating PSEUDO-R2 (VARIANCE REDUCTION RATE)

```{r i2-calc}
# 1. Extract variance components from both models
# Note: In metafor's rma.mv, sigma2[1] is Level 3 (Between-study) 
# and sigma2[2] is Level 2 (Within-study/Between-trial)

sigma2_L3_null <- res_null$sigma2[1]
sigma2_L2_null <- res_null$sigma2[2]

sigma2_L3_optimal <- rescue_model$sigma2[1]
sigma2_L2_optimal <- rescue_model$sigma2[2]

# 2. Calculate Pseudo-R2 for each level
pseudo_R2_L3 <- (sigma2_L3_null - sigma2_L3_optimal) / sigma2_L3_null * 100
pseudo_R2_L2 <- (sigma2_L2_null - sigma2_L2_optimal) / sigma2_L2_null * 100

# 3. Print the results beautifully
cat(sprintf("
==============================================================================
📊 META-REGRESSION VARIANCE REDUCTION REPORT (Pseudo-R²)
==============================================================================
Level 3 Variance (Between-Study / First_Author):
  - Null Model   : %.4f
  - Optimal Model: %.4f
  - Pseudo-R²    : %.2f%%

Level 2 Variance (Within-Study / Between-Trial):
  - Null Model   : %.4f
  - Optimal Model: %.4f
  - Pseudo-R²    : %.2f%%
==============================================================================
", 
sigma2_L3_null, sigma2_L3_optimal, pseudo_R2_L3,
sigma2_L2_null, sigma2_L2_optimal, pseudo_R2_L2))
```


# 🌲 11. Visualizations & Post-Hoc Analysis

Once the model is fitted, we can generate publication-quality forest plots.
```{r}
#| label: fig-forest
#| fig-cap: "Three-level meta-analysis forest plot"
#| fig-width: 10
#| fig-height: 4.5
#| dev: "pdf"
#| warning: false
#| message: false

# ==========================================
# 1. Load packages and read data
# ==========================================
library(dplyr)
library(metafor)

my_data <- cleaned_data

# ==========================================
# 2. Aggregate data at the study level
# ==========================================
study_data <- my_data %>%
  group_by(DOI, First_Author, Pub_Year) %>%
  summarize(
    mj = n(),
    yi = sum(yi / vi, na.rm = TRUE) / sum(1 / vi, na.rm = TRUE),
    vi = 1 / sum(1 / vi, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  arrange(yi) %>%
  mutate(study_label = paste0(First_Author, " et al. ", Pub_Year))

# ==========================================
# 3. Fit three-level meta-analysis model
# ==========================================
res_3level <- rma.mv(
  yi, vi,
  random = ~ 1 | DOI/Trial,
  data = my_data,
  test = "knha"
)

overall_yi <- as.numeric(res_3level$beta)

# ==========================================
# 4. Generate forest plot (Quarto Handles the Device!)
# ==========================================

par(mar = c(5, 4, 3, 2))

forest(
  x = study_data$yi, vi = study_data$vi, transf = transf.ilogit,
  slab = study_data$study_label, ilab = study_data$mj,
  ilab.xpos = -0.25, ilab.pos = 4, xlim = c(-0.8, 1.4), alim = c(0, 1),
  at = seq(0, 1, by = 0.25), ylim = c(-2.5, nrow(study_data) + 3),
  refline = transf.ilogit(overall_yi), lty = c("solid", "dotted"),
  pch = 15, cex = 0.9, header = FALSE, efac = 0,
  xlab = "Overall accuracy", showweights = FALSE
)

# Add zebra striping
for (i in seq(1, nrow(study_data), by = 2)) {
  rect(xleft = -2, ybottom = i - 0.5, xright = 2, ytop = i + 0.5,
       col = "#0000001A", border = NA)
}

# Add layout lines and headers
abline(h = nrow(study_data) + 1, col = "black", lwd = 1, lty = "solid")
abline(h = 0, col = "black", lwd = 1, lty = "solid")

text(-0.8, nrow(study_data) + 1.8, "Study", pos = 4, font = 2)
text(-0.25, nrow(study_data) + 1.8, "mj", pos = 4, font = 2)
text(1.4, nrow(study_data) + 1.8, "Proportion [95% CI]", pos = 2, font = 2)

# Add overall diamond
addpoly(
  res_3level, transf = transf.ilogit, row = -1.2,
  mlab = "Three-level meta-analysis", col = "black"
)

text(-0.25, -1.2, sum(study_data$mj), pos = 4)
```

