
## 📂 1. Environment Setup & Data Ingestion

First, we need to load the required library (`metafor`) and read the processed data extracted from Phase 2.

```{r}
#| label: setup-and-load
# Install readxl if you haven't: install.packages("readxl")
library(metafor)
library(readxl)
library(here)
library(dplyr)
```

## 📊 2. Data Preview

Let's read the Excel sheet and take a look at the column structures.
*(Uncomment the lines below once your Excel file has data)*

```{r}
# ==============================================================================
# 1. Load Dataset
# ==============================================================================
data_path <- here("data", "processed", "06_manually_checked_for_R.xlsx")
my_data <- read_excel(data_path)

# ==============================================================================
# 2. Preprocessing Logic
# ==============================================================================

# Locate the index range for metric columns (from 'Accuracy_Top1' to the second-to-last column)
start_idx <- which(names(my_data) == "Accuracy_Top1")
metric_cols <- names(my_data)[start_idx:(ncol(my_data) - 1)]

# Count valid numeric entries per metric (as.numeric automatically coerces "Unknown" to NA)
counts <- suppressWarnings(sapply(my_data[metric_cols], function(x) sum(!is.na(as.numeric(x)))))

# Select the metric with the highest count of valid numeric data as the single target $y$ variable
best_metric <- names(which.max(counts))

# Print the selection summary to the console
cat("🏆 Selected target $y$ variable:", best_metric, "(Valid numeric records:", max(counts), ")\n")

# ==============================================================================
# 3. Data Cleaning & Pipeline Execution
# ==============================================================================
# Pipeline: Convert target to numeric -> Filter out NAs -> Select base features + target + last column
processed_data <- my_data %>% 
  mutate(!!best_metric := suppressWarnings(as.numeric(.data[[best_metric]]))) %>% 
  filter(!is.na(.data[[best_metric]])) %>% 
  select(1:(start_idx - 1), all_of(best_metric), last_col())

# ==============================================================================
# 4. Inspection & Quality Check
# ==============================================================================
cat("\n✅ Data cleaning complete! Retained the final column:", names(processed_data)[ncol(processed_data)], "\n")
cat("Final Dataset Dimensions:", dim(processed_data)[1], "rows,", ncol(processed_data), "columns\n")

# Preview the clean tibble
head(processed_data)
```

```{r}


```

## 🧠 3. Three-Level Meta-Analysis Modeling

We will use the `rma.mv` function from the `metafor` package to fit our three-level random-effects model. This accounts for the hierarchical structure (e.g., multiple effect sizes extracted from the same study).

```{r}
#| label: meta-model
# Example structure for 3-level meta-analysis:
# res <- rma.mv(yi = effect_size, 
#               V = sampling_variance, 
#               random = ~ 1 | study_id / effect_id, 
#               data = my_data)
# summary(res)

```

## 🌲 4. Visualizations (Forest & Funnel Plots)

Once the model is fitted, we can generate publication-quality forest plots.

```{r}
#| label: plots
# forest(res)
# funnel(res)

```

```

