## 📂 1. Environment Setup & Data Ingestion

First, we need to load the required packages and read the processed data extracted from Phase 2.

```{r, warning=FALSE, message=FALSE}
#| label: setup-and-load
library(metafor)
library(readxl)
library(here)
library(dplyr)
library(tidyr)
```

## 📊 2. Data Loading & Target Variable Selection

Let's read the Excel sheet and identify the performance metric with the most valid entries to serve as our target variable $y$.

```{r}
#| label: data-loading
# 1. Load Dataset
data_path <- here("data", "processed", "06_manually_checked_for_R.xlsx")
my_data <- read_excel(data_path)

# 2. Preprocessing Logic: Select best metric
start_idx <- which(names(my_data) == "Accuracy_Top1")
metric_cols <- names(my_data)[start_idx:(ncol(my_data) - 1)]

# Count valid numeric entries per metric
counts <- suppressWarnings(sapply(my_data[metric_cols], function(x) sum(!is.na(as.numeric(x)))))
best_metric <- names(which.max(counts))

cat("🏆 Selected target $y$ variable:", best_metric, "(Valid numeric records:", max(counts), ")\n")

# 3. Target Extraction & Initial Filter
processed_data <- my_data %>% 
  mutate(!!best_metric := suppressWarnings(as.numeric(.data[[best_metric]]))) %>% 
  filter(!is.na(.data[[best_metric]])) %>% 
  select(1:(start_idx - 1), all_of(best_metric), last_col())

cat("\n✅ Initial cleaning complete! Retained the final column:", names(processed_data)[ncol(processed_data)], "\n")
cat("Dimensions before feature standardization:", dim(processed_data)[1], "rows,", ncol(processed_data), "columns\n")
```

## 🧹 3. Feature Engineering & Standardization

Here we consolidate all string manipulation, data binning, and factor conversions into a single, highly efficient `dplyr` pipeline.

```{r}
#| label: data-standardization
processed_data <- processed_data %>%
  mutate(
    # --- 1. Num_Classes (Categorical Binning) ---
    Num_Classes_Numeric = as.numeric(na_if(Num_Classes, "Unknown")),
    Num_Classes = factor(
      case_when(
        # in my case, all 'NA' in a paper, manually label them as "Massive"
        First_Author == "Abdaoui" ~ "Massive", 
        Num_Classes_Numeric < 20 ~ "Small",
        Num_Classes_Numeric >= 20 & Num_Classes_Numeric <= 100 ~ "Medium",
        Num_Classes_Numeric > 100 & Num_Classes_Numeric <= 1000 ~ "Large",
        Num_Classes_Numeric > 1000 ~ "Massive"
      ),
      levels = c( "Small", "Medium", "Large", "Massive"),
      ordered = TRUE
    ),
    
    # --- 2. Data_Source ---
    Data_Source = case_when(
      grepl("MIMIC|google|IPA", Data_Source, ignore.case = TRUE) ~ "Open_Non_Gov",
      grepl("Census|IRS|SEER|NCI", Data_Source, ignore.case = TRUE) ~ "Regulated_Gov",
      TRUE ~ "Private"
    ),
    
    # --- 3. Train_N (Log10 Transformation) ---
    # Safely converts "Unknown"(non-numeric) to NA, then takes log10
    Train_N = log10(as.numeric((Train_N))),
    
    # --- 4. Avg_Text_Length ---
    Avg_Text_Length = case_when(
      grepl("Short|2\\.76|3\\.78", Avg_Text_Length, ignore.case = TRUE) ~ "Short Text",
      grepl("439|3000|500|Full|Narrative", Avg_Text_Length, ignore.case = TRUE) ~ "Long Document",
      TRUE ~ "Not Reported"
    ),
    
    # --- 5. Imbalance_Ratio (Severity Levels) ---
    Imbalance_Ratio = case_when(
      grepl("≤5|Zipfian|n<10|Top 10%|highly skewed", Imbalance_Ratio, ignore.case = TRUE) ~ "3_Severe_LongTail",
      grepl("seldom reported|disproportionate|Max freq 8, Min freq 2 occurrences", Imbalance_Ratio, ignore.case = TRUE) ~ "2_Moderate",
      grepl("Unknown|Not Reported", Imbalance_Ratio, ignore.case = TRUE) ~ 'Unknown',
      TRUE ~ "1_balanced"
    ),
    
    # --- 6. Base_Model (Core Model Extraction) ---
    Base_Model = case_when(
      grepl("BERT", Base_Model, ignore.case = TRUE) ~ "BERT",
      grepl("T5", Base_Model, ignore.case = TRUE) ~ "T5",
      grepl("LLaMA", Base_Model, ignore.case = TRUE) ~ "LLaMA",
      grepl("MTHISAN", Base_Model, ignore.case = TRUE) ~ "MTHISAN",
      grepl("Retrieval|BEACON", Base_Model, ignore.case = TRUE) ~ "Information Retrieval",
      grepl("Logistic|LR", Base_Model, ignore.case = TRUE) ~ "Logistic Regression",
      grepl("Naïve|Bayes|MNB", Base_Model, ignore.case = TRUE) ~ "Naive Bayes",
      grepl("SVM", Base_Model, ignore.case = TRUE) ~ "SVM",
      grepl("Forest|LightGBM", Base_Model, ignore.case = TRUE) ~ "Tree Ensemble",
      grepl("Knn", Base_Model, ignore.case = TRUE) ~ "KNN",
      grepl("Lasso|Elastic|SGD|Perceptron", Base_Model, ignore.case = TRUE) ~ "Linear/Regularized",
      TRUE ~ "Other"
    ),
    
    # --- 7. Model_Approach (Flat vs Hierarchical) ---
    Model_Approach = case_when(
      grepl("Hierarchical", Model_Approach, ignore.case = TRUE) ~ "Hierarchical",
      grepl("Flat", Model_Approach, ignore.case = TRUE) ~ "Flat",
      TRUE ~ Model_Approach
    ),
    
    # --- 8. Cross-Validation (CV) ---
    CV_Applied = case_when(
      grepl("yes", CV_Applied, ignore.case = TRUE) ~ "Yes",
      grepl("no", CV_Applied, ignore.case = TRUE) ~ "No",
      TRUE ~ 'Not reported'
    ),
    CV_Folds = as.numeric(CV_Folds),
    
    # --- 9. Hyperparam_Tuning ---
    Hyperparam_Tuning = case_when(
      grepl("Grid Search|Grid search", Hyperparam_Tuning, ignore.case = TRUE) ~ "Grid Search",
      grepl("Manual", Hyperparam_Tuning, ignore.case = TRUE) ~ "Manual Tuning",
      grepl("Self-tuning", Hyperparam_Tuning, ignore.case = TRUE) ~ "Self-Tuning",
      grepl("Not Reported|Unknown", Hyperparam_Tuning, ignore.case = TRUE) ~ "Not Reported",
      TRUE ~ "Not Reported"
    ),
    
    # --- 10. Factorize Binary Columns ---
    Human_in_Loop = factor(Human_in_Loop, levels = c(0,1), labels = c('No','Yes')),
    Open_Source   = factor(Open_Source, levels = c(0,1), labels = c('No','Yes')),
    Hierarch_Metric = factor(Hierarch_Metric, levels = c(0,1), labels = c('No','Yes'))
  ) %>%
  
  # --- 11. Strategy Flags to Yes/No ---
  mutate(across(starts_with("Strategy_"), ~ ifelse(. == 1, "Yes", "No"))) %>%
  
  # rename train size since it was log-transformed
  rename(log10_Train_N = Train_N) %>%
  
  # Clean up intermediate calculation columns
  select(-Num_Classes_Numeric)
```

## ✂️ 4. Drop Zero-Variance Columns

Remove any columns that ended up having exactly 1 unique value across the entire dataset, as they provide no variance for statistical modeling.

```{r}
#| label: drop-constant-cols
# Identify columns with exactly 1 unique value (ignoring NAs)
constant_cols <- names(processed_data)[sapply(processed_data, function(x) length(unique(na.omit(x))) == 1)]

cat("🗑️ Deleted columns due to zero variance:", paste(constant_cols, collapse = ", "), "\n")

# Drop these columns to create the final modeling dataset
modeling_data <- processed_data %>% select(-all_of(constant_cols))

# Factors transformation
modeling_data <- modeling_data %>% 
  mutate(across(where(is.character), as.factor))

# clear view
summary(modeling_data)
```

## 5.  drop the redundant prdictors
```{r}
# ==============================================================================
# Step 1: Dro High Missingness & Low Variance Variables First
# ========================= =====================================================
  cleaned_data = modeling_data %>% select(
    -Prompt_Engineering,     # 92.5% Missing / Zero Variance
    -CV_Folds,              # 83.3% Missing
    - Strategy_Data_level, # near zero variance (No: 51 Yes: 3)
    - Open_Source,         # near zero variance (No: 51 Yes: 3)
    - Taxonomy_Structure,  # near zero variance (hierarchical: 49 flat: 5)
    - Model_Approach,      # near zero variance (Flat: 49 Hierarchical: 5 )
    ) 
```
```{r}
# ==============================================================================
# 🚨 STAGE 2: SINGLE-AUTHOR NESTED CATEGORY SCAN
# ==============================================================================
library(dplyr)

cat("\n=================================================================\n")
cat(" 🚨 STAGE 2: SINGLE-AUTHOR NESTED CATEGORY CHECK\n")
cat("=================================================================\n")
# This scan detects if any category belongs EXCLUSIVELY to a single author.
# Such nesting makes it impossible for rma.mv to distinguish the fixed effect
# of the category from the random effect of the author, causing fatal singularities.

# Extract all categorical variables
cat_vars <-  cleaned_data %>% 
  select(where(is.character) | where(is.factor)) %>%
  select(-any_of(c("DOI", "First_Author", "Trial")))

found_nested_vars <- FALSE

for (col_name in names(cat_vars)) {
  
  # Create a cross-tabulation of First_Author vs the current variable
  cross_tab <- table(cleaned_data$First_Author, cat_vars[[col_name]])
  
  # Calculate how many distinct authors use each category (count non-zero rows per column)
  authors_per_cat <- colSums(cross_tab > 0)
  
  # Find categories that exist in exactly ONE author
  nested_cats <- names(authors_per_cat)[authors_per_cat == 1]
  
  if (length(nested_cats) > 0) {
    found_nested_vars <- TRUE
    cat(sprintf("\n⚠️ WARNING: Variable [%s] has categories strictly nested within a single author!\n", col_name))
    
    for (cat_name in nested_cats) {
      # Identify which specific author holds this category
      author_name <- rownames(cross_tab)[cross_tab[, cat_name] > 0]
      # Get the number of samples for this category
      n_samples <- cross_tab[author_name, cat_name]
      
      cat(sprintf("   👉 Category '%s' (n = %d) is 100%% exclusive to author '%s'.\n", 
                  cat_name, n_samples, author_name))
    }
    
    # Print the full cross-tabulation table to let the user see the exact distribution
    cat(sprintf("\n📊 Full Distribution Table for [%s] across Authors:\n", col_name))
    print(cross_tab)
    cat("-----------------------------------------------------------------\n")
  }
}

if (!found_nested_vars) {
  cat("✅ PASSED! No single-author nested categories detected. Your features span across multiple clusters safely.\n")
}
```
```{r}
# ==============================================================================
# 🛠️ STAGE 2: Recode & Merge Variables to Resolve Single-Author Nesting
# ==============================================================================
cleaned_data <- cleaned_data %>%
  mutate(
    # 1. Domain: Medical (disease) vs Non-Medical (industry, occupation, product)
    Domain = factor(case_when(
      grepl("disease", Domain, ignore.case = TRUE) ~ "Medical",
      TRUE ~ "Non-Medical"
    )),
    
    # 2. Language: English vs Non-English (French, Turkish)
    Language = factor(case_when(
      grepl("english", Language, ignore.case = TRUE) ~ "English",
      TRUE ~ "Non-English"
    )),
    
    # 3. Taxonomy_Depth: Combine Top_Level and Intermediate to break nesting
    Taxonomy_Depth = factor(case_when(
      Taxonomy_Depth %in% c("Top_Level", "Intermediate") ~ "Reduced_Depth",
      TRUE ~ "Full_Resolution"
    )),
    
    # 4. NLP_Era: Group into broad historical paradigms
    NLP_Era = factor(case_when(
      NLP_Era %in% c("Traditional ML", "Deep Learning (pre-PLM)") ~ "Pre-Transfer",
      NLP_Era %in% c("PLM", "LLM") ~ "Transfer-Based",
      TRUE ~ as.character(NLP_Era) # Safety fallback
    )),
    
    # 5. Hyperparam_Tuning: Binary grouping to absorb single-author categories
    # (Merges Grid Search, Manual Tuning, and Self-Tuning into one "Reported" group)
    Hyperparam_Tuning = factor(case_when(
      Hyperparam_Tuning == "Not Reported" ~ "Not_Reported",
      TRUE ~ "Reported_Tuning"
    ))
  ) %>%
  
  select(
    -Class_System,         # Fragmented across 8 specific systems
    -Base_Model,           # Highly specific to authors (e.g., MTHISAN)
    -Feature_Extraction,   # 'Static Embeddings' 100% nested
    -Adaptation_Strategy   # 'PEFT/LoRA' 100% nested
  )

# Verify the new structure
cat("\n✅ Data transformation complete. Current dimensions:", dim(cleaned_data), "\n")
```
```{r}
# 🗑️ STAGE 3: Drop Highly Fragmented & Unsalvageable Variables
#| label: cramers-v-heatmap

# 1. Install and load the corrplot package if you haven't already
# install.packages("corrplot")
library(corrplot)
library(dplyr)

# 2. Select all categorical (factor/character) variables and drop identifiers
cat_vars <- cleaned_data  %>% 
  select(where(is.factor) | where(is.character)) %>%
  select(-any_of(c("DOI", "First_Author", "Trial"))) # Remove non-feature columns

# 3. Initialize an empty matrix for Cramer's V values
n <- ncol(cat_vars)
cramer_matrix <- matrix(1, nrow = n, ncol = n, 
                        dimnames = list(names(cat_vars), names(cat_vars)))

# 4. Compute pairwise Cramer's V using Chi-Square statistic
for (i in 1:(n - 1)) {
  for (j in (i + 1):n) {
    tbl <- table(cat_vars[[i]], cat_vars[[j]])
    # CRITICAL FIX: We add [ correct = FALSE ] to prevent R from automatically 
    # shrinking the Chi-Square statistic for 2x2 tables with small cell counts (n < 5).
    # This restores the true mathematical 1.00 correlation for perfectly aligned features.
    chi2 <- suppressWarnings(chisq.test(tbl, correct = FALSE)$statistic)
    v <- sqrt(chi2 / (sum(tbl) * min(nrow(tbl) - 1, ncol(tbl) - 1)))
    # Handle any potential NaN/NA safely
    cramer_matrix[i, j] <- cramer_matrix[j, i] <- ifelse(is.na(v) || is.nan(v), 0, v)
  }
}

# 5. Plot the publication-quality heatmap
corrplot(cramer_matrix, 
         method = "color",        # Use colored squares
         type = "upper",          # Show only the upper triangle to avoid redundancy
         tl.col = "black",        # Text label color
         tl.srt = 45,             # Rotate text labels by 45 degrees
         addCoef.col = "darkgray",# Add exact Cramer's V values inside the squares
         number.cex = 0.6,        # Size of the coefficient text
         title = "Categorical Feature Association (Cramer's V)",
         mar = c(0, 0, 2, 0))     # Adjust margins to fully display the title

```
```{r}
# ==============================================================================
# 1. Automatically Group Collinear Variables into Disjoint Clusters
# ==============================================================================
var_names <- colnames(cramer_matrix)
visited <- setNames(rep(FALSE, length(var_names)), var_names)
cluster_id <- 1
final_clusters <- list()

for (v in var_names) {
  if (!visited[v]) {
    # Find all variables that belong to the same equivalence class (Cramer's V > 0.99)
    # Thanks to transitivity, scanning one row captures the entire cluster perfectly.
    group <- var_names[cramer_matrix[v, ] > 0.99 & !is.na(cramer_matrix[v, ])]
    
    # Mark the whole gang as visited so we don't repeat
    visited[group] <- TRUE
    
    # We only care about clusters that have redundant variables (size > 1)
    if (length(group) > 1) {
      
      # Calculate Degrees of Freedom (DF = unique categories - 1) for each member
      cluster_df <- data.frame(
        Cluster_ID = paste0("Cluster_", cluster_id),
        Variable   = group,
        DF         = sapply(group, function(x) length(unique(na.omit(modeling_data[[x]]))) - 1),
        stringsAsFactors = FALSE
      )
      
      # Sort the cluster members: Smallest DF comes first (Best Representative)
      cluster_df <- cluster_df[order(cluster_df$DF), ]
      
      # Generate exact tactical action recommendations for your thesis
      cluster_df$Action_Recommendation <- c("KEEP (Best Representative)", 
                                             rep("DROP (Redundant Info)", nrow(cluster_df) - 1))
      
      final_clusters[[length(final_clusters) + 1]] <- cluster_df
      cluster_id <- cluster_id + 1
    }
  }
}

# ==============================================================================
# 2. Print the Beautiful, Consolidated "Decision Sheet"
# ==============================================================================
if (length(final_clusters) > 0) {
  decision_sheet <- do.call(rbind, final_clusters)
  cat("\n🏆 CONSOLIDATED FEATURE REDUCTION DECISION SHEET 🏆\n")
  cat("==============================================================================\n")
  print(decision_sheet, row.names = FALSE)
  cat("==============================================================================\n")
} else {
  cat("✅ Clean space! No redundant clusters detected.\n")
}
```

## 6.  drop the redundant prdictors
```{r}
cleaned_data <- cleaned_data %>%
  select(
   
    # cluster 3
    -Human_in_Loop,)
````
```{r}
library(car)
# delate 'log10_Train_N'，Avg_Text_Length
lm_vif_clean_v2 <- lm(yi ~ Taxonomy_Depth + Classification_Logic + 
                     Num_Classes + Data_Source + Language  + Domain + Imbalance_Ratio +
                     Strategy_Cost_Sensitive + Strategy_Taxonomy_Mod + 
                     Strategy_Post_Hoc + Strategy_None + 
                     Domain_Specific + 
                     NLP_Era + CV_Applied + Hyperparam_Tuning,
                      data = cleaned_data)

# 2. 验证（这一步很重要，如果它输出 Empty，说明终于干净了！）
cat("\n--- 🔍 Checking for Aliased Variables ---\n")
print(alias(lm_vif_clean_v2))

# 3. make sure all GVIF^(1/(2*Df)) small 5
vif(lm_vif_clean_v2)
  
  ```



## 📈 6. Target Variable Distribution & Transformation

Checking the distribution of our target accuracy variable to see if standardizations (Logit or Arcsine Square Root) improve normality for Meta-Regression.

```{r, fig.width=12, fig.height=4}
#| label: target-distribution
y <- modeling_data[[best_metric]]

# Set up a 1x3 grid for side-by-side comparison
par(mfrow = c(1, 3))

# 1. Raw Distribution
hist(y, col="skyblue", border="white",
     main = "Raw Distribution", 
     xlab = "Accuracy Score", ylab = "Frequency") 

# 2. Logit Transformation
hist(log(y/(1-y)), col="lightgreen", border="white",
     main = "Logit Transformation", 
     xlab = "Logit(Accuracy)", ylab = "Frequency") 

# 3. Arcsine Square Root Transformation
hist(asin(sqrt(y)), col="salmon", border="white",
     main = "Arcsine Sqrt Transformation", 
     xlab = "Asin(Sqrt(Accuracy))", ylab = "Frequency")

# Reset layout
par(mfrow = c(1, 1))
```

```{r}
library(metafor)
# ==============================================================================
# 1. Calculate Effect Size (Logit) and Sampling Variance
# ==============================================================================
cleaned_data <- cleaned_data %>%
  mutate(
    Test_N = as.numeric(Test_N),
    p = Accuracy_Top1
  ) %>%
  filter(!is.na(Test_N) & !is.na(p)) %>%
  mutate(
    # Safety boundary: Prevent log(0) or division by zero for perfect scores
    p_adj = case_when(
      p == 1.0 ~ 0.9999,
      p == 0.0 ~ 0.0001,
      TRUE ~ p
    ),
    
    # Calculate Logit Effect Size (yi)
    yi = log(p_adj / (1 - p_adj)),
    
    # Calculate Sampling Variance (vi)
    vi = 1 / (Test_N * p_adj * (1 - p_adj))
  )
```

```{r}
library(metafor)
library(dplyr)

# 1. Define all candidate predictors (Full Model scope)
candidate_vars <- c(
  "Taxonomy_Depth", "Classification_Logic", "Num_Classes", "Data_Source", 
  "Language", "Domain", "Imbalance_Ratio", "Strategy_Cost_Sensitive", 
  "Strategy_Taxonomy_Mod", "Strategy_Post_Hoc", "Strategy_None", 
  "Domain_Specific", "NLP_Era", "CV_Applied", "Hyperparam_Tuning"
)
# 1. Base Null Model
null_model <- rma.mv(yi = yi, V = vi, mods = ~ 1, 
                     random = ~ 1 | First_Author / Trial, 
                     method = "ML", data = cleaned_data,
                     control = list(iter.max = 30, rel.tol = 1e-5))
cat("🎯 [Baseline] Null Model BIC =", round(BIC(null_model), 2), "\n\n")

# 2. Scout Round 1
r1_results <- data.frame(Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)

for (var in candidate_vars) {
  fmla <- as.formula(paste("yi ~", var))
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  
  if (!is.null(mdl)) {
    r1_results <- rbind(r1_results, data.frame(Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
  }
}

# Print the Round 1 Leaderboard
cat("📊 ROUND 1 LEADERBOARD (Look for the LOWEST BIC):\n")
print(r1_results %>% arrange(BIC), row.names = FALSE)
```
```{r}
# ==============================================================================
# Chunk 2: Round 2 Scouting (Pairing the Winner of Round 1 with Remainder)
# ==============================================================================
# ✍️ HUMAN ACTION: Put the winning variable from Round 1 inside c() below:
current_model_vars <- c("Strategy_None") 

remaining_vars <- setdiff(candidate_vars, current_model_vars)
r2_results <- data.frame(Added_Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)

for (var in remaining_vars) {
  test_vars <- c(current_model_vars, var)
  fmla <- as.formula(paste("yi ~", paste(test_vars, collapse = " + ")))
  
  # Canary check to avoid collinearity within pairs
  if (any(is.na(coef(lm(fmla, data = cleaned_data))))) next
  
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  
  if (!is.null(mdl)) {
    r2_results <- rbind(r2_results, data.frame(Added_Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
  }
}

# Print the Round 2 Leaderboard
cat("📊 ROUND 2 LEADERBOARD (Compare with your Round 1 baseline BIC):\n")
print(r2_results %>% arrange(BIC), row.names = FALSE)
```
```{r}
# ==============================================================================
# Chunk 3: Round 3 Scouting (Fixing Strategy_None + Imbalance_Ratio)
# ==============================================================================
# ✍️ HUMAN ACTION: Both winners are now locked in together
current_model_vars <- c("Strategy_None", "Imbalance_Ratio") 

remaining_vars <- setdiff(candidate_vars, current_model_vars)
r3_results <- data.frame(Added_Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)

for (var in remaining_vars) {
  test_vars <- c(current_model_vars, var)
  fmla <- as.formula(paste("yi ~", paste(test_vars, collapse = " + ")))
  
  # Canary check to avoid collinearity within the trio
  if (any(is.na(coef(lm(fmla, data = cleaned_data))))) next
  
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  
  if (!is.null(mdl)) {
    r3_results <- rbind(r3_results, data.frame(Added_Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
  }
}

# Print the Round 3 Leaderboard
cat("📊 ROUND 3 LEADERBOARD (Compare with your Round 2 baseline BIC: 182.95):\n")
print(r3_results %>% arrange(BIC), row.names = FALSE)
```

```{r}
# ==============================================================================
# Chunk 4: Round 4 Scouting (Forcing Strategy_None + Imbalance_Ratio + Data_Source)
# ==============================================================================

# ✍️ HUMAN ACTION: Forcing the top 3 into the model
current_model_vars <- c("Strategy_None", "Imbalance_Ratio", "Data_Source") 

remaining_vars <- setdiff(candidate_vars, current_model_vars)
r4_results <- data.frame(Added_Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)

for (var in remaining_vars) {
  test_vars <- c(current_model_vars, var)
  fmla <- as.formula(paste("yi ~", paste(test_vars, collapse = " + ")))
  
  # Canary check to avoid collinearity within the quad
  if (any(is.na(coef(lm(fmla, data = cleaned_data))))) next
  
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  
  if (!is.null(mdl)) {
    r4_results <- rbind(r4_results, data.frame(Added_Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
  }
}

# Print the Round 4 Leaderboard
cat("📊 ROUND 4 LEADERBOARD (Compare with your Round 3 baseline BIC: 182.51):\n")
print(r4_results %>% arrange(BIC), row.names = FALSE)
```

```{r}
# ==============================================================================
# Chunk 5: Round 5 Scouting (Forcing the Quad-Squad)
# ==============================================================================

# ✍️ Locked in the 4 winners
current_model_vars <- c("Strategy_None", "Imbalance_Ratio", "Data_Source", "Hyperparam_Tuning") 

remaining_vars <- setdiff(candidate_vars, current_model_vars)
r5_results <- data.frame(Added_Variable = character(), BIC = numeric(), QMp = numeric(), stringsAsFactors = FALSE)

for (var in remaining_vars) {
  test_vars <- c(current_model_vars, var)
  fmla <- as.formula(paste("yi ~", paste(test_vars, collapse = " + ")))
  if (any(is.na(coef(lm(fmla, data = cleaned_data))))) next
  
  mdl <- tryCatch({
    rma.mv(yi = yi, V = vi, mods = fmla, random = ~ 1 | First_Author / Trial, 
           method = "ML", data = cleaned_data, control = list(iter.max = 30))
  }, error = function(e) NULL)
  
  if (!is.null(mdl)) {
    r5_results <- rbind(r5_results, data.frame(Added_Variable = var, BIC = round(BIC(mdl), 2), QMp = round(mdl$QMp, 4)))
  }
}

cat("📊 ROUND 5 LEADERBOARD (Compare with your Round 4 baseline BIC: 181.47):\n")
print(r5_results %>% arrange(BIC), row.names = FALSE)
```

```{r}
# ==============================================================================
# 🌟 RESCUE: Final Multivariable Model with Knapp-Hartung Adjustment
# ==============================================================================
library(metafor)

cat("==============================================================================\n")
cat("🔥 RUNNING RESCUE MODEL: Standard REML with Knapp-Hartung (test='knha')\n")
cat("==============================================================================\n")

# Use the same Fatal Four predictors
final_fmla <- as.formula("yi ~ Strategy_None + Imbalance_Ratio + Data_Source + Hyperparam_Tuning")

# Refit using REML with Knapp-Hartung adjustment (The gold standard for small k)
# We drop the robust() wrapper because N_clusters = 8 is too small for CRVE asymptotic assumptions.
rescue_model <- rma.mv(yi = yi, V = vi, mods = final_fmla, 
                       random = ~ 1 | First_Author / Trial, 
                       method = "REML", test = "knha", # 👈 CRITICAL: Small-sample correction
                       data = cleaned_data,
                       control = list(iter.max = 100))

# Print the real publication table
print(rescue_model)
```

```{r}
# ==============================================================================
# 📊 Safe Model Comparison: Null vs. Optimal (100% Crash-Proof)
# ==============================================================================

cat("==============================================================================\n")
cat("⏳ Fitting Null and Optimal Models using 'ML' Method safely...\n")
cat("==============================================================================\n")

# 1. Null Model (Baseline)
model_null_ml <- rma.mv(yi = yi, V = vi, mods = ~ 1, 
                        random = ~ 1 | First_Author / Trial, 
                        method = "ML", data = cleaned_data,)

# 2. Optimal Model (Your 4 stepwise winners)
fmla_optimal <- as.formula("yi ~ Strategy_None + Imbalance_Ratio + Data_Source + Hyperparam_Tuning")
model_optimal_ml <- rma.mv(yi = yi, V = vi, mods = fmla_optimal, 
                           random = ~ 1 | First_Author / Trial, 
                           method = "ML", data = cleaned_data,)


anova(model_null_ml, model_optimal_ml)
# Warning message: REML comparisons not meaningful for models with different fixed effects
# (use 'refit=TRUE' to refit both models based on ML estimation). 
````
```{r}
# 3. Full Model (All 15 stable predictors to show global variance)
fmla_full <- as.formula("yi ~ Domain + Taxonomy_Depth + Classification_Logic + 
                        Num_Classes + Data_Source + Language  + 
                        Imbalance_Ratio + Strategy_Cost_Sensitive + 
                        Strategy_Taxonomy_Mod + Strategy_Post_Hoc + 
                        Strategy_None + NLP_Era + Domain_Specific + CV_Applied + Hyperparam_Tuning")
model_full_ml <- rma.mv(yi = yi, V = vi, mods = fmla_full, 
                        random = ~ 1 | First_Author / Trial, 
                        method = "ML", data = cleaned_data)

# ==============================================================================
# 🏆 The Holy Grail: Likelihood Ratio Test & Information Criteria Comparison
# ==============================================================================
cat("\n🏆 MODEL COMPARISON RESULTS 🏆\n")
cat("==============================================================================\n")

# metafor's anova() automatically handles nested model testing and prints AIC/BIC
anova(model_optimal_ml, model_full_ml)
anova(model_null_ml, model_full_ml) # FULL model BIC 194.4703 close  Null 195.6626
```



```{r}
# Step 2: Multi-level Meta-Regression with CRVE
cat("\n--- CRVE Meta-Regression Results for Model 1 ---\n")
meta_model_1 <- rma.mv(yi = yi, V = vi, 
                       mods = ~ Taxonomy_Depth + Classification_Logic + 
                     Num_Classes + Data_Source + Language + 
                     log10_Train_N + Avg_Text_Length + Imbalance_Ratio + 
                     Strategy_Cost_Sensitive + Strategy_Taxonomy_Mod + 
                     Strategy_Post_Hoc + Strategy_None + 
                     Domain_Specific + Feature_Extraction + Adaptation_Strategy + CV_Applied + Hyperparam_Tuning, 
                       random = ~ 1 | First_Author / Trial, 
                       data = cleaned_data, 
                       method = "REML")bk
print(meta_model_1)
```



## 🧠 7. Three-Level Meta-Analysis Modeling

We will use the `rma.mv` function from the `metafor` package to fit our three-level random-effects model. This accounts for the hierarchical structure (e.g., multiple effect sizes extracted from the same study).



```{r}
# ==============================================================================
# 2. Fit the Three-Level Null Meta-Analysis Model
# ==============================================================================
# Fit an intercept-only (null) model in the Logit space.
# Random effects structure accounts for dependencies within the same paper.
# Level 3: First_Author (Between-study variance)
# Level 2: Trial (Between-model variance within the same study)

res_null <- rma.mv(yi = yi, 
                   V = vi, 
                   random = ~ 1 | First_Author / Trial, 
                   data = cleaned_data,
                   method = "REML", test = "knha")

# Print the model summary (Logit Scale)
cat("--- Null Model Results (Logit Scale) ---\n")
summary(res_null)
```
```{r}
# ==============================================================================
# 3. Back-transformation to Original Accuracy Scale
# ==============================================================================
# Use the inverse logit function to convert the pooled estimate and CIs 
# back to a 0-1 proportion.

cat("\n\n--- Pooled Accuracy (Back-transformed to 0-1 scale) ---\n")
predict(res_null, transf = transf.ilogit)
```
```{r}
# ==============================================================================
# Calculate I^2 (Variance Proportions) for the 3-Level Meta-Analysis
# ==============================================================================

# 1. 提取三层的方差 (Variance components)
sigma2_3 <- res_null$sigma2[1] # Level 3 (First_Author)
sigma2_2 <- res_null$sigma2[2] # Level 2 (Trial)

# 2. 计算 Level 1 的典型抽样误差 (Typical sampling variance, v)
# 采用 Higgins & Thompson (2002) 的经典近似算法
wi <- 1 / modeling_data$vi
k <- length(wi)
v_typical <- (k - 1) / (sum(wi) - (sum(wi^2) / sum(wi)))

# 3. 计算三层的总方差
total_variance <- sigma2_3 + sigma2_2 + v_typical

# 4. 计算并打印 I^2 百分比
I2_Level3 <- (sigma2_3 / total_variance) * 100
I2_Level2 <- (sigma2_2 / total_variance) * 100
I2_Level1 <- (v_typical / total_variance) * 100

cat("--- Distribution of Variance (I^2 in 3-Level Model) ---\n")
cat(sprintf("Level 3 (Between-Study / First_Author) : %.2f%%\n", I2_Level3))
cat(sprintf("Level 2 (Within-Study / Trial)         : %.2f%%\n", I2_Level2))
cat(sprintf("Level 1 (Sampling Error)               : %.2f%%\n", I2_Level1))
cat(sprintf("Total True Heterogeneity (I^2)         : %.2f%%\n", I2_Level3 + I2_Level2))
```

```{r}

```

## 🌲 7. Visualizations & Crosstabs

Once the model is fitted, we can generate publication-quality forest plots. We can also inspect interactions between categorical predictors.

```{r}
#| label: plots-and-tables
# forest(res)
# funnel(res)

# Cross-tabulation example
table(modeling_data$Imbalance_Ratio, modeling_data$Imbalance_Strategy)
```

